### 2014-12-02 writing/F'14 paper/intro.tex
Paper update, bug fixes.
Revised intro

To date, experimental investigations of these concepts using 
distributed representations have been largely confined to short phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment}.
For robust natural language understanding, it is essential to model
these phenomena in their full generality on complex linguistic
structures. Other recent work \cite{grefenstette2013towards,rocktaschellow} has
developed well-understood frameworks that can compute the meanings of 
certain fragments of natural language compositionally from vector or
tensor representations. These frameworks are too structured to allow broad
coverage meaning representations to be learned in
supervised natural language tasks, and as such do not provide direct insight
into the question of what existing applied machine learning models are 
capable of.

% TODO: Any way to avoid nested parens?

Our research uses the task of \ii{natural language
  inference} (also known as \ii{recognizing textual entailment}
\cite{dagan2006pascal}), in which the goal is to determine the core
inferential relationship between two sentences. Much of the
theoretical work on this task (and some successful implemented models
\cite{maccartney2009extended,watanabe2012latent}) involves \ii{natural
  logics}, which are formal systems that define rules of inference
between natural language words, phrases, and sentences without the
need of intermediate representations in an artificial logical
language. We use the natural logic developed by MacCartney and Manning 
\shortcite{maccartney2009extended} 
as our formal model. This logic defines seven core relations of synonymy, 
entailment, contradiction, and mutual consistency, as summarized in
Table~\ref{b-table}, and it provides rules of semantic combination for
projecting these relations from the lexicon up to complex phrases. The
formal properties and inferential strength of this system are now
well-understood \cite{Icard:Moss:2013,Icard:Moss:2013:LILT}.

% TODO: Do we need both of these Icard/Moss citations?

Since no existing model architecture can be adopted without modification
to handle entailment classification, we describe a novel method for this task
in the spirit of prior work on recursive neural networks (\ref{methods}).
In three experiments, we use this pre-specified logical grammar to
generate controlled data sets encoding the semantic relationships
between pairs of expressions and evaluate whether models with this architecture can 
learn to correctly identify the relationships between novel pairs.
In our first experiment (Section~\ref{sec:join}), we
evaluate the ability of these models to learn the core relational
algebra of natural logic from data. Our second experiment
(Section~\ref{sec:recursion}) extends this evaluation to relations
between complex recursive structures like $(a \plor b)$ and
$\plneg (\plneg a \pland \plneg b)$, and our third experiment
(Section~\ref{sec:quantifiers}) involves relations between quantified
statements like \ii{every reptile walks} and \ii{no turtle moves}.
We find that the plain recursive NN achieves only mixed results in all three
experiments, whereas the stronger RNTN model generalizes well in every
case, suggesting that it has in fact learned, or at least learned to
simulate, our target logical concepts. These experiments provide the 
most convincing demonstration to date of the ability of neural networks to model
semantic inferences in complex natural language sentences.

Finally, we perform a simple additional experiment to verify that our novel
model structure is able to show similar reasoning behavior on real natural language data.
The small size of existing entailment data precludes a state-of-the-art result, but we show
that our model is able to perform competitively on the SICK entailment challenge, suggesting
that the representational abilities that we observe in the previous sections are not limited to 
narrowly defined artificial tasks.

\begin{table*}[tp]
  \centering
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{l c l l} 
    \toprule
    Name & Symbol & Set-theoretic definition & Example \\ 
    \midrule
    entailment         & $x \natfor y$   & $x \subset y$ & \ii{turtle, reptile}  \\ 
    reverse entailment & $x \natrev y$   & $x \supset y$ & \ii{reptile, turtle}  \\ 
    equivalence        & $x \nateq y$    & $x = y$       & \ii{couch, sofa} \\ 
    alternation        & $x \natalt y$   & $x \cap y = \emptyset \wedge x \cup y \neq \mathcal{D}$ & \ii{turtle, warthog} \\ 
    negation           & $x \natneg y$   & $x \cap y = \emptyset \wedge x \cup y = \mathcal{D}$    & \ii{able, unable} \\
    cover              & $x \natcov y$   & $x \cap y \neq \emptyset \wedge x \cup y = \mathcal{D}$ & \ii{animal, non-turtle} \\ 
    independence       & $x \natind y$   & (else) & \ii{turtle, pet}\\
    \bottomrule
  \end{tabular}
  \caption{\label{b-table}The seven natural logic relations of MacCartney and Manning \protect\shortcite{maccartney2009extended}. 
    $\mathcal{D}$ is the universe of possible objects of the same type as those being compared, 
    and the relation $\natind$ applies whenever none of the other six do.} %, including when there 
    %is insufficient knowledge to choose a label.}

>>>>

To date, experimental investigations of these concepts using
distributed representations have been largely confined to short
phrases
\cite{Mitchell:Lapata:2010,Grefenstette-etal:2011,baroni2012entailment}.
However, for robust natural language understanding, it is essential to
model these phenomena in their full generality on complex linguistic
structures. Other recent work
\cite{grefenstette2013towards,rocktaschellow} has developed rich
frameworks for computing the meanings of complex fragments of natural
language compositionally from vector or tensor representations, but
these approaches do not confront the question of how to learn their
highly structured representations from data using existing applied
machine learning models.

% TODO: Any way to avoid nested parens? Yes, use \citealt ---CP

Our research uses the task of \ii{natural language
  inference} (also known as \ii{recognizing textual entailment}; 
\citealt{dagan2006pascal}), in which the goal is to determine the core
inferential relationship between two sentences. Much of the
theoretical work on this task (and some successful implemented models; 
\citealt{maccartney2009extended,watanabe2012latent}) involves \ii{natural
  logics}, which are formal systems that define rules of inference
between natural language words, phrases, and sentences without the
need of intermediate representations in an artificial logical
language. We use the natural logic developed by
\newcite{maccartney2009extended} as our formal model. This logic
defines seven core relations of synonymy, entailment, contradiction,
and mutual consistency, as summarized in Table~\ref{b-table}, and it
provides rules of semantic combination for projecting these relations
from the lexicon up to complex phrases. The formal properties and
inferential strength of this system are now well-understood
\cite{Icard:Moss:2013,Icard:Moss:2013:LILT}.

% TODO: Do we need both of these Icard/Moss citations? -- I'd prefer
% to keep them ---CP.

% Since no existing model architecture can be adopted without modification
% to handle entailment classification, we describe a novel method for this task
% in the spirit of prior work on recursive neural networks (\ref{methods}).
In our first set of experiments, we use this pre-specified logical
grammar to generate controlled data sets encoding the semantic
relationships between pairs of expressions and evaluate whether each
of two classes of neural model---plain RNNs and recursive neural
tensor networks (RNTNs; \cite{socher2013acl1})---can learn those
relationships correctly. In our first experiment
(Section~\ref{sec:join}), we evaluate the ability of these models to
learn the core relational algebra of natural logic from data. Our
second experiment (Section~\ref{sec:recursion}) extends this
evaluation to relations between complex recursive structures like
$(a \plor b)$ and $\plneg (\plneg a \pland \plneg b)$, and our third
experiment (Section~\ref{sec:quantifiers}) involves relations between
quantified statements like \ii{every reptile walks} and \ii{no turtle
  moves}. \tbchecked{We find that the plain recursive NN achieves only
  mixed results in all three experiments, whereas the stronger RNTN
  model generalizes well in every case, suggesting that it has in fact
  learned, or at least learned to simulate, our target logical
  concepts.}

The experiments with simulated data provide a convincing demonstration
of the ability of neural networks to learn to encode semantic
inferences in complex natural language sentences from reasonably-sized
training sets. However, we are also interested in the more practical
question of whether they can learn these representations from more
naturalistic text. To address this question, we apply our models to
the SICK entailment challenge data. The small size of this corpus puts
data-intensive neural models like ours at a disadvantage, but we are
nonetheless able to achieve competitive performance on it
\mynote{CONSIDER ADDING A CONCRETE DETAIL --- E.G., ACCURACY
  AND ITS RELATION TO THE COMPETITION MEDIAN}, suggesting that the
representational abilities that we observe in the previous sections
are not limited to carefully circumscribed tasks.

\begin{table*}[tp]
  \centering\small
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1}
  \begin{tabular}{l c l l} 
    \toprule
    Name & Symbol & Set-theoretic definition & Example \\ 
    \midrule
    entailment         & $x \natfor y$   & $x \subset y$ & \ii{turtle, reptile}  \\ 
    reverse entailment & $x \natrev y$   & $x \supset y$ & \ii{reptile, turtle}  \\ 
    equivalence        & $x \nateq y$    & $x = y$       & \ii{couch, sofa} \\ 
    alternation        & $x \natalt y$   & $x \cap y = \emptyset \wedge x \cup y \neq \mathcal{D}$ & \ii{turtle, warthog} \\ 
    negation           & $x \natneg y$   & $x \cap y = \emptyset \wedge x \cup y = \mathcal{D}$    & \ii{able, unable} \\
    cover              & $x \natcov y$   & $x \cap y \neq \emptyset \wedge x \cup y = \mathcal{D}$ & \ii{animal, non-turtle} \\ 
    independence       & $x \natind y$   & (else) & \ii{turtle, pet}\\
    \bottomrule
  \end{tabular}
  \caption{\label{b-table}The seven natural logic relations of MacCartney and Manning \protect\shortcite{maccartney2009extended}. 
    $\mathcal{D}$ is the universe of possible objects of the same type as those being compared, 
    and the relation $\natind$ applies whenever none of the other six do.} %, including when there 
    %is insufficient knowledge to choose a label.}
